\myTitle

### 2024-07-15 body-text-of-paper.tex
small edit

\section*{Acknowledgements}
Research was supported in part by the USDA-APHIS-National Feral Swine Damage
Management Program. We are grateful for the numerous Wildlife Services and Missouri
Department of Conservation employees that contributed to genetic sampling of wild pigs
within southeastern Missouri. We thank Yniv Palti for providing flanking sequences and the linkage map for 57K markers for making a recombination map for the steelhead/cutthroat trout example. Writing of this paper was facilitated by the Mobile High Altitude Venue for Ecological Analysis,
Genetics and Statistics, through which ECA, MGD, and TJS were scientists-in-residence on location near
Cheyenne, WY for 3 days in October 2023. This is contribution number mHAVEAGAS-003.
This work utilized the Alpine high performance computing resource at the University of Colorado Boulder.
Alpine is jointly funded by the University of Colorado Boulder, the University of Colorado Anschutz, Colorado State University,
and the National Science Foundation (award 2201538). 
The findings and conclusions in this publication are those of the author(s) and should not be construed to represent any official USDA or U.S. Government determination or policy. This research was supported in part by the U.S. Department of Agriculture, Animal Plant Inspection Service, Wildlife Services, National Wildlife Research Center.

>>>>

\section*{Acknowledgements}
Research was supported in part by the USDA-APHIS-National Feral Swine Damage
Management Program. We are grateful for the numerous Wildlife Services and Missouri
Department of Conservation employees that contributed to genetic sampling of wild pigs
within southeastern Missouri. We thank Yniv Palti for providing flanking sequences and the linkage map for 57K markers for making a recombination map for the steelhead/cutthroat trout example. Writing of this paper was facilitated by the mobile High Altitude Venue for Ecological Analysis,
Genetics and Statistics, through which ECA, MGD, and TJS were scientists-in-residence on location near
Cheyenne, WY for 3 days in October 2023. This is contribution number mHAVEAGAS-003.
This work utilized the Alpine high performance computing resource at the University of Colorado Boulder.
Alpine is jointly funded by the University of Colorado Boulder, the University of Colorado Anschutz, Colorado State University,
and the National Science Foundation (award 2201538). 
The findings and conclusions in this publication are those of the author(s) and should not be construed to represent any official USDA or U.S. Government determination or policy. This research was supported in part by the U.S. Department of Agriculture, Animal Plant Inspection Service, Wildlife Services, National Wildlife Research Center.
